BurgerTown Presents: Open Adcess

### 2017-04-09 paper-sponsorships.tex
a couple small modifications to three files

\subsection{Call for Advertisements}
Reach the largest holistic-minded audience in the entire northeastern United
States with an ad in the next ACM edition.
Our readership is mostly devoid of energy vampires and is therefore suitable
for empath advertisers.
Where IEEE uses Western proof verification techniques, our broad minded
audience validates mathematical claims in an intuitive holistic manner and will
bring that same spirit into evaluating the claims of your advertisements.
Our readers will engage with your brand through meditation and other
surprises.

>>>>

\subsection{Call for Advertisements}
Reach the largest holistic-minded audience in the entire northeastern United
States with an ad in the next ACM edition.\footnote{Wisdom disputes this claim, but we have the narrow computational tools to prove our publication and community have way more holism.}
Our readership is mostly devoid of energy vampires and is therefore suitable
for empath advertisers.
Where IEEE uses Western proof verification techniques, our broad minded
audience validates mathematical claims in an intuitive holistic manner and will
bring that same spirit into evaluating the claims of your advertisements.
Our readers will engage with your brand through meditation and other
surprises.

### 2017-04-09 related-work.tex
a couple small modifications to three files

Rapidshare \cite{rapidshare} was a website that provided rate-limited free
downloads while simultaneously selling a paid download service that was
superior to the free tier.
This technique was meant to entice users to pay for the service.
Unfortunately, as Rapidshare no longer exists, it seems that this technique, used alone, is insufficient to cover the costs of running a download service. Or maybe they did not take this technique far enough. He he he.

Free weeklies such as \emph{Wisdom} \cite{wisdom} employ such heavy use of print ads,
native ads, and classifieds that they may be distributed without charge to health food stores, food cooperatives, and participating Sheetz locations.
We also adopt these techniques to embed in all of our papers in
\autoref{sec:sponsors}.

>>>>

Rapidshare \cite{rapidshare} was a website that provided rate-limited free
downloads while simultaneously selling a paid download service that was
superior to the free tier.
This technique was meant to entice users to pay for the service.
Unfortunately, as Rapidshare no longer exists it seems that this technique, used alone,
alone is insufficient to cover the costs of running a download service. Or maybe they did not take this idea far enough. He he he.

Wisdom \cite{wisdom} and many other free rags make such heavy use of traditional print ads,
native ads, and classifieds that paper copies may profitably be distributed without charge to health food stores, food cooperatives, and participating Sheetz locations.
We also adopt these techniques to embed in all of our papers in
\autoref{sec:sponsors}.
Additionally, Wisdom claims most holism but we have the narrow computational
tools to prove that we are more holistic.
